### 2016-03-29 Chapters/chap3/Manuscript-FINAL.tex
Correct bib for uppercase

\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}

@@

% \subsection{Construction and parameterization}
Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.

@@

\section{Localized Property of the Primary Lanzcos Mode}

We have established  that the Primary Lanzcos Mode is more like the normal modes of the isolated
donor and acceptor moieties, rather than of the entire molecule. The relation between the
PLM and bond length change partially verifies our statement.
In this section, we explore  the localization in greater detail.
First, we project the PLM onto the normal modes of entire molecule,
which is shown in Fig.~\ref{LancProj}, as a comparison to Fig.~\ref{fragProj}, where the normal modes of the individual moieties are used.    It is clear that on the basis of entire molecule, more modes are significantly involved.   This is in contrast to the projection of the PLM onto only the local modes of the isolated moieties, only a handful modes contribute.  Since the PLM  best captures the initial nuclear dynamics,
 its close relation with local sites reveals the fact that the exciton transfer here is more like a local excitation/de-excitation
coupled by exchange interaction,  in accordance with the Dexter mechanism \cite{dexter1953theory}.

>>>>

\chapter{Chapter 3}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}

@@

% \subsection{Construction and parameterization}
% Our method was detailed in ~Ref. \cite{yang2014intramolecular} but to be self-contained, we briefly present it here.

@@

\section{Localized Property of the Primary Lanczos Mode}

We have established  that the primary Lanczos mode is more like the normal modes of the isolated
donor and acceptor moieties, rather than of the entire molecule. The relation between the
PLM and bond length change partially verifies our statement.
In this section, we explore  the localization in greater detail.
First, we project the PLM onto the normal modes of entire molecule,
which is shown in Fig.~\ref{LancProj}, as a comparison to Fig.~\ref{fragProj}, where the normal modes of the individual moieties are used.    It is clear that on the basis of entire molecule, more modes are significantly involved.   This is in contrast to the projection of the PLM onto only the local modes of the isolated moieties, only a handful modes contribute.  Since the PLM  best captures the initial nuclear dynamics,
 its close relation with local sites reveals the fact that the exciton transfer here is more like a local excitation/de-excitation
coupled by exchange interaction,  in accordance with the Dexter mechanism \cite{dexter1953theory}.
